%-------------------------
% Resume in LaTeX
% Author: Jake Gutierrez (with cleanup)
% Based on: https://github.com/sb2nov/resume
% License: MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

% Packages
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{xcolor}
\input{glyphtounicode}

% Font options commented out for reference
% Sans-serif options:
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}
% 
% Serif options:
% \usepackage{CormorantGaramond}
% \usepackage{charter}

% Page setup
\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

% Layout settings
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}

% Ensure PDF is machine readable/ATS parsable
\pdfgentounicode=1

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{#1 \vspace{-2pt}}
}

\newcommand{\classesList}[4]{
  \item\small{#1 #2 #3 #4 \vspace{-2pt}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
  \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & \textbf{\small #2} \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
  \item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textit{\small#1} & \textit{\small #2} \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
  \item
  \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & \textbf{\small #2}\\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

% List settings
\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
  {\Huge \scshape Parik Kukreja} \\ \vspace{1pt}
  6242 Chatham Dr S, Seattle, WA 98118 \\ \vspace{1pt}
  \small 
  \raisebox{-0.1\height}\faPhone\ 206-883-1615 ~ 
  \href{mailto:kukrejaparik@gmail.com}{\raisebox{-0.2\height}\faEnvelope\ \underline{kukrejaparik@gmail.com}} ~ 
  \href{https://linkedin.com/in/parikkukreja/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/parikkukreja}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {University of Washington, Seattle}{Expected Graduation: Spring 2027}
    {Bachelor of Science in Computer Science; GPA: 3.8}{Seattle, Washington}
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart
  \resumeSubheading
    {Starfish Space}{September 2025 -- December 2025}
    {Incoming Flight Software Engineer}{Seattle, WA}
    
  \resumeSubheading
    {Amazon}{June 2025 -- September 2025}
    {Incoming SDE Intern}{Sunnyvale, CA}
    
  \resumeSubheading
    {Roby}{June 2024 -- October 2024}
    {Software Engineering Intern}{Seattle, WA}
    \resumeItemListStart
      \resumeItem{Spearheaded the end-to-end development of a Python-based automation tool for mapping HVAC unit IDs to corresponding room names, leveraging Google Cloud Vision's AI for image recognition.}
      \resumeItem{Optimized image preprocessing using Python libraries like OpenCV and PIL, improving the quality of optical character recognition in floor plans and BMS screenshots.}
      \resumeItem{Developed the frontend using React for dynamic interfaces, Tailwind CSS for responsive design, and JavaScript for interactivity. Integrated with a Flask backend to handle API requests and data flow.}
      \resumeItem{Delivered a highly effective end product, deployed in the company's GPT interface, that accurately linked HVAC unit IDs to corresponding rooms with up to 95\% accuracy, significantly enhancing the efficiency and precision of building management processes.}
    \resumeItemListEnd

  \resumeSubheading
    {Armoire}{June 2024 -- August 2024}
    {Software Engineering Intern}{Seattle, WA}
    \resumeItemListStart
      \resumeItem{Streamlined the checkout process, implementing several key improvements that resulted in a 10\% decrease in shopping cart abandonment rate.}
      \resumeItem{Enhanced internal tools, resulting in faster processing times and successfully locating and correcting 800+ units of misplaced or misidentified inventory.}
      \resumeItem{Overhauled the six-year-old Stylist Catwalk Tool, optimizing code structure and enhancing overall performance to boost efficiency for stylists.}
      \resumeItem{Leveraged a comprehensive set of development tools including GitHub for version control and collaboration, Docker for consistent environment management, and AWS Elastic Beanstalk for automated deployment and application monitoring.}
    \resumeItemListEnd
    
  \resumeSubheading
    {WiBotic}{October 2022 -- November 2022}
    {Engineering Intern}{Seattle, WA}
    \resumeItemListStart
      \resumeItem{Assembled over 50 charging modules from raw parts and blueprints, ensuring precise alignment with engineering specifications.}
      \resumeItem{Conducted rigorous testing of each charging module to validate functionality and adherence to quality standards.}
      \resumeItem{Catalogued and managed over 5,000 units of inventory using SOS inventory manager, maintaining an organized and up-to-date parts database.}
    \resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Extracurricular Activities/Outside Coursework}
\vspace{-5pt}
\resumeSubHeadingListStart
  \resumeProjectHeading
    {\textbf{Introduction to Quantum Computing (July 2022 - August 2022): }}{}
    \resumeItemListStart
      \resumeItem{Gained an introductory knowledge of quantum computing through daily lectures, labs, and homework assignments. Class covered linear algebra, coding with Qiskit, quantum mechanics, quantum algorithms, and quantum applications.}
    \resumeItemListEnd
    
  \resumeProjectHeading
    {\textbf{Inspirit AI Scholars Live Online (June 2022 -- July 2022): }}{}
    \resumeItemListStart
      \resumeItem{Learned basic AI and ML concepts over the course of 25 hours of instruction and guided coding, culminating in designing, training, and testing a model to identify human emotion expressed in images.}
    \resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-15pt}

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    \textbf{Languages}{: Python, Java, HTML/CSS, JavaScript, SQL, C, C++} \\
    \textbf{Developer Tools}{: GIT, VS Code, Google Cloud Vision API, PyCharm, Sentry.io, Cursor} \\
    \textbf{Technologies/Frameworks}{: WSL, GitHub, JUnit, Docker, AWS Elastic Beanstalk, Node.js, Django, OpenCV}
  }}
\end{itemize}
\vspace{-16pt}

%-----------HOBBIES---------------
\section{Hobbies/Interests - \small Magic: the Gathering, (American) Football, Swimming, Online Gaming, Tom Petty}
\vspace{-16pt}

\end{document}
